Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-19 man/tables/t_dendro_summary.Rmd
update tables

---
output:
  word_document:
    fig_caption: yes
    highlight: null
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

>>>>

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

### 2018-11-19 man/tables/t_droughts.Rmd
update tables

---
output: 
  word_document:
    fig_caption: yes
    highlight: null
    reference_docx: ../../templates/template_pagebreak.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

colnames(dys) <- c("Duration \n(months)", "Intensity", "Severity", "Lowest SPEI", "Months", "Year")

pander(dys)
```

>>>>

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

td <- regulartable(dys, col_keys = names(dys))
td <- td %>% 
  set_header_labels(d_duration = "Duration \n(months)", d_intensity = "Intensity", 
                   d_severity = "Severity", lowest_spei = "Lowest \nSPEI", rangeDate = "Months", year = "Year") %>% 
  align(align = "center", part ="all") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 10) %>%
  fontsize(part = "body", size = 9) 
td
```

### 2018-11-19 man/tables/t_robust_anovas.Rmd
update tables

---
output:
  word_document:
    fig_caption: yes
    highlight: null
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

@@

mti <- mt %>% 
  autofit() %>% 
  empty_blanks() %>% 
  align(j = 1,  align = "center") %>% 
  merge_v(~variable) %>% 
  set_header_labels(variable = "", factores = "", rt_F = "Resistance", rt_p = "Resistance", rc_F = "Recovery", rc_p = "Recovery", rs_F = "Resilience", rs_p = "Resilience") %>% 
  add_header(variable = "Variable", factores = "Factor", rt_F = "F", rt_p = "p", rc_F = "F", rc_p = "p", rs_F = "F", rs_p = "p", top = FALSE) %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 12) %>%
  fontsize(part = "body", size = 11) %>% 
  width(j = 2, width = 2) %>% 
  italic(i = ~ rt_p < 0.01, j = ~ rt_p) %>% 
  italic(i = ~ rc_p < 0.01, j = ~ rc_p) %>% 
  italic(i = ~ rs_p < 0.01, j = ~ rs_p)
mti

# mt <- set_formatter(mt, 
#                     rt_F = function(x) format(round(x, 1)),
#                     rc_F = function(x) format(round(x, 1)),
#                     rs_F = function(x) format(round(x, 1))
#                     ) 
# 
# mt

>>>>

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

mti <- mt %>% 
  autofit() %>% 
  empty_blanks() %>% 
  align(j = 1,  align = "center") %>% 
  merge_v(~variable) %>% 
  set_header_labels(variable = "", factores = "", rt_F = "Resistance", rt_p = "Resistance", rc_F = "Recovery", rc_p = "Recovery", rs_F = "Resilience", rs_p = "Resilience") %>% 
  add_header(variable = "Variable", factores = "Factor", rt_F = "F", rt_p = "p", rc_F = "F", rc_p = "p", rs_F = "F", rs_p = "p", top = FALSE) %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 10) %>%
  fontsize(part = "body", size = 9) %>% 
  width(j = 2, width = 2) %>% 
  italic(i = ~ rt_p < 0.01, j = ~ rt_p) %>% 
  italic(i = ~ rc_p < 0.01, j = ~ rc_p) %>% 
  italic(i = ~ rs_p < 0.01, j = ~ rs_p) %>% 
  merge_at(i = 1, j=4:5, part="header") %>% 
  merge_at(i = 1, j=7:8, part="header") %>% 
  merge_at(i = 1, j=10:11, part="header")

mti
# mt <- set_formatter(mt, 
#                     rt_F = function(x) format(round(x, 1)),
#                     rc_F = function(x) format(round(x, 1)),
#                     rs_F = function(x) format(round(x, 1))
#                     ) 
# 
# mt

### 2018-11-19 man/tables/t_sampled_plots.Rmd
update tables

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
```

@@

@@

ta <- ta %>% set_header_labels(name = "Site", lat_m = "Lat (\u00B0)", long_m = "Long (\u00B0)", 
                               elev = "Elevation\n(m)", slope = "Slope (\u00B0)",  prec = "Prec.\n(mm)",
                               temp = "Temp.\n(\u00B0 C)", n_trees = "# trees\n(# cores)", dn = "Dbh (cm)",
                               h = "Height\n(m)", age = "Age\n(years)", dn_all = "Dbh all\n(cm)", 
                               h_all = "Height all\n(m)", ba = "BA\n(m2/ha)", 
                               stand_density = "Density\n(trees/ha)", srd = "SRD") %>% 
  add_header(name="", lat_m ="", long_m="", elev="", slope ="", prec = "", temp = "",
             n_trees = "Cored trees", dn = "Cored trees", h = "Cored trees", age = "Cored trees", 
             dn_all = "Competence", h_all = "Competence", ba = "Competence", 
             stand_density = "Competence", srd = "Competence", top = TRUE) %>% 
  merge_at(i = 1, j =c(8:11) , part = "header") %>% 
  merge_at(i = 1, j =c(12:16) , part = "header") %>% 
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(i= 1, part = "header", size = 8) %>% 
  fontsize(i= 2, part = "header", size = 8) %>% 
  italic(i=1, part = "header") %>% 
    # General format 
  fontsize(part = "body", size = 7) %>% 
  autofit(add_w = 0) %>% 
  align(align = "center") %>% 
  width(j = c(2,3), width = 0.35) %>% 
  width(j = c(6,7,8), width = 0.6)

ta

>>>>

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library(officer)
```

@@

std_border = fp_border(width = 1)

@@

ta <- ta %>% set_header_labels(name = "Site", lat_m = "Lat (\u00B0)", long_m = "Long (\u00B0)", 
                               elev = "Elevation\n(m)", slope = "Slope (\u00B0)",  prec = "Prec.\n(mm)",
                               temp = "Temp.\n(\u00B0 C)", n_trees = "# trees\n(# cores)", dn = "Dbh (cm)",
                               h = "Height\n(m)", age = "Age\n(years)", dn_all = "Dbh all\n(cm)", 
                               h_all = "Height all\n(m)", ba = "BA\n(m2/ha)", 
                               stand_density = "Density\n(trees/ha)", srd = "SRD") %>% 
  add_header(name="", lat_m ="", long_m="", elev="", slope ="", prec = "", temp = "",
             n_trees = "Cored trees", dn = "Cored trees", h = "Cored trees", age = "Cored trees", 
             dn_all = "Competence", h_all = "Competence", ba = "Competence", 
             stand_density = "Competence", srd = "Competence", top = TRUE) %>% 
  merge_at(i = 1, j =c(8:11) , part = "header") %>% 
  merge_at(i = 1, j =c(12:16) , part = "header") %>% 
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(i= 1, part = "header", size = 8) %>% 
  fontsize(i= 2, part = "header", size = 8) %>% 
  italic(i=1, part = "header") %>% 
    # General format 
  fontsize(part = "body", size = 8) %>% 
  autofit(add_w = 0) %>% 
  align(align = "center") %>% 
  width(j = c(2,3), width = 0.35) %>% 
  width(j = c(6,7,8), width = 0.6)

ta %>% 
   vline(j = c(7, 11), border = std_border, part="all")
